A New Metric for the Analysis of Swarms using Potential Fields

### 2018-08-20 paper.tex
Minor Revisions

\section{Inter-Agent Distance metric}\label{Section:DistanceDynamics}
The inter-agent distance metric considers a swarm in terms of how the agents are physically distributed: i.e. only the inter-agent distances and their standard deviation are considered. The standard deviation indicates the extent to which the swarm is out of balance and therefore the degree of movement required to re-balance the swarm structure. If the standard deviation is zero then all the agents are evenly spaced.

@@

Navarro and Fernando describe a \textit{mean distance error} metric that is based on the variations in distances between inter-agent spaces~\cite{NIM:09}. This is the same as the standard deviation of the distance based internal movement metric.

>>>>

\section{Inter-Agent Distance metric}\label{Section:DistanceDynamics}
The inter-agent distance metric considers a swarm in terms of how the agents are physically distributed: i.e. only the inter-agent distances and their standard deviation are considered. The standard deviation indicates the extent to which the swarm is out of balance and therefore the degree of movement required to rebalance the swarm structure. If the standard deviation is zero then all the agents are evenly spaced.

@@

Navarro and Fernando describe a \textit{mean distance error} metric that is based on the variations in distances between inter-agent spaces~\cite{NIM:09}. This is the same as the standard deviation of the distance-based internal movement metric.
